---
title: "nirmitin_FinalHomeworkCode_01"
author: "Nirmiti Naik"
date: "16 September 2021"
output: html_document
---
<br>
The stringr package is installed so that the command str_split() will work. 
```{r}
library(stringr)
```

## **Challenge 1**
<br> 
First, I assigned v1 to the given first line of "Ulysses"" by James Joyce
``` {r challenge 1 final i}
v1 <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
```

Then, I removed the punctuation so that the vector can eventually be comprised of only one word character strings and assigned the result to x
``` {r challenge 1 final ii}
x <- gsub("[[:punct:]]","",v1)
x
```

Next, I split the vector into one word character strings using str_split() from the stringr package and assigned the result to y
```{r challenge 1 final iii}
y <- str_split(x, boundary("word"))
y
```

Finally, I used a sequence command to extract every third element from a matrix m composed of the vector y
``` {r challenge 1 final iv}
m <- matrix(data= c("Stately","plump","Buck","Mulligan","came","from","the","stairhead","bearing","a","bowl","of","lather","on","which","a","mirror","and","a","razor","lay","crossed"))
m[seq(from = 1, to = 22, by = 3)]
```

## **Challenge 2**
<br>
I recreated the given matrix that the columns will eventually be extracted from.
```{r challenge 2 final i}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```
First, I extracted the 2nd, 3rd, and 6th columns and assigned them to the variable x.
```{r challenge 2 final ii}
x <- m[,c(2,3,6)]
x
```
Then, I extracted the 6th to 8th row and assigned them to the variable x. 
```{r challenge 2 final iii}
x <- m[(6:8),]
x
```
Finally, I extracted the elements from row 2, column 2 to row 6, column 9 and assigned them to the variable x.
``` {r challenge 2 final iv}
x <- m[2:6,2:9]
x
```

# **Challenge 3**
<br>
First, I created an 4-dimensional, 400 element array (5 x 5 x 4 x 4) array a with the elements being 400 to 1 in descending order
``` {r challenge 3 final i}
a <-array(data = 400:1, dim = c(5,5,4,4))
a
```
The result of a[1,1,1,2] would be the element at position [1,1] in the [,,1,2] matrix
```{r challenge 3 final ii}
a[1,1,1,2]
```
The result of a[2,3,2,] would be the elements at position [2,3] in the [,,2,] matrices
```{r challenge 3 final iii}
a[2,3,2,]
```
The result of a[1:5,1:5,3,3] is the elements at positions from row 1, column 1 to row 5, column 5 in the [,,3,3] matrix
```{r challenge 3 final iv}
a[1:5,1:5,3,3] 
```

# **Challenge 4**
<br>
First, I used the given example of the Strepsirhini as a base to work off of 
``` {r challenge 4 final i}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
```
Then, I coded the two innermost/most evolved lists: Platyrrhini and Catarrhini (which fall under Anthropoidea) with the intention that these lists would be the most nested so it would make sense to establish them first
``` {r challenge 4 final ii}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
```
Next, I coded a list for Tarsioidea which falls under Haplorhini along with Anthropoidea
``` {r challenge 4 final iii}
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
```
Finally, I ended with the broadest/all encompassing list (Primates) so that it would be able to take all the previously created lists (contained under Haplorhini and Strepsirhini) under it to branch off
``` {r challenge 4 final iv}
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")

Primates
```

## **Challenge 5**
<br>
The peer commentary I receieved was especially helpful for this challenge and allowed me to better understand the problem itself and how to use the various as.__() commands. 

To begin with, I stored 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2 in a 5x3 row-wise matrix m3. 
``` {r challenge 5 final i} 
m3<-matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
```
Then, I coerced the matrix into a data frame.
``` {r challenge final ii}
m3.df <- as.data.frame(m3)
m3.df
```
Next, I used as.logical() to coerce the second column to be logical-valued. 
``` {r challenge final iii}
m3.df$V2<-as.logical(m3.df[,2])
m3.df
```
Following this,I used as.factor() to coerce the third column to be factor-valued
``` {r challenge final iv}
m3.df$V3<-as.factor(m3.df[,3])
m3.df
```
Finally, I used the str() command to show the data type for each variable in my dataframe
``` {r challenge final v}
str(m3.df)
```
<br>
<br>